%-------------------------
% Resume in Latex
% Author : Vidushi Wahal
% Modified: Amir Nazemi
%------------------------

\documentclass[letterpaper,11pt]{article}
\sloppy
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage{color}
\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}
\hypersetup{
    colorlinks=true,
    linkcolor=blue,
    filecolor=magenta,      
    urlcolor=gray,
    }
\usepackage[english]{babel}
\usepackage{graphicx}
\usepackage{array}
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    {#1}{#2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-1pt}\\
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#3} & \textit{\small #4} 
    \end{tabular*}\vspace{-5 pt}
}

\newcommand{\resumeSubheadingLong}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-1pt}\\
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#3} & \textit{\small #4} 
    \end{tabular*}\vspace{-12pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
\textbf{{\LARGE Amir Nazemi, Ph.D.}} &\vspace{6pt}
\\
  LinkedIn : \href{https://www.linkedin.com/in/amir-nazemi-edu/}{\underline{https://www.linkedin.com/in/amir-nazemi-edu/}}& Email : \href{mailto:amir.nazemi@uwaterloo.ca}{\underline{amir.nazemi@uwaterloo.ca}} \vspace{1pt}\\ 
 Portfolio: \href{http://amirnazemi.com/}{\underline{http://amirnazemi.com/}} &  Mobile : +1(226) 581-4634 \vspace{1pt}\\ Orcid: \href{https://orcid.org/0000-0002-8405-473X}{\underline{https://orcid.org/0000-0002-8405-473X}} &  Waterloo, ON, Canada \\
\end{tabular*}

%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
  
    \resumeSubheadingLong
      {Postdoctoral Researcher}{University of Waterloo, Canada}
      {Systems Design Engineering}{2024 – present}
      \vspace{1px}
      \resumeItemListStart
     {Sport Analytics Research Group, Homography estimation, Puck detection, Player action recognition, Game event detection}
    \resumeItemListEnd 

    \resumeSubheadingLong
      {Postdoctoral Researcher}{University of Waterloo, Canada}
      {Systems Design Engineering}{2023 – 2024}
      \vspace{1px}
      \resumeItemListStart
     {AI for Medical Data, Diffusion Models for Inverse Problems, Video Understanding, AI for Dietary Data}
    \resumeItemListEnd 

    \resumeSubheadingLong
      {Doctor of Philosophy (Ph.D.)}{University of Waterloo, Canada}
      {Systems Design Engineering}{2019 – 2023}
      \vspace{1px}
      \resumeItemListStart
     Thesis: {Continual Learning-based Video Object Segmentation}
    \newline
     GPA: 91/100
    \resumeItemListEnd
    
    \resumeSubheadingLong
      {Master of Science (M.Sc.)}{Shiraz University, Iran}
      {Artificial Intelligence}{2011 – 2014}
      \vspace{1px}
      \resumeItemListStart
      Thesis: {Object Recognition via Sparse Coding}
      \newline
      GPA: 90/100
    \resumeItemListEnd
    
    \resumeSubheadingLong
      {Bachelor (B.Sc.)}{Shahid Bahonar University of Kerman, Iran}
      {Computer Software Engineering}{2006 – 2010}
      \vspace{1px}
      \resumeItemListStart
      Thesis: {Multi-National Particle Swarm Optimization Algorithm}
        \newline
      GPA: 78/100
    \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------Teaching Experience------------
\section{Teaching Experience and Certificates}
\resumeSubHeadingListStart
    \resumeSubheading
      {University of Waterloo}{Waterloo, Canada}
      {Lecturer}{2022}
      \resumeItemListStart
      \resumeItem{{Statistical Image Processing and Multidimensional Modeling (SYDE 672)}}
          {}
        \begin{itemize}
        \item {Graduate level course for PhD and M.Sc students.}
        \item{Course perception surveys scores: 4.1/5.}
        \item{Inverse problems, multidimensional modeling, large-scale statistical problems, generative models}
          \end{itemize}
      \resumeItemListEnd

    \resumeSubheading
      {University of Waterloo}{Waterloo, Canada}
      {Center for Teaching Excellence (CTE)}{2021 - 2022}
      \resumeItemListStart
      \resumeItem{{Fundamentals of University Teaching (FUT) Certificate.}}
          {}
        \begin{itemize}
        \item{Three microteaching sessions.}
        \item{Six workshops: Teaching methods; Effective lesson plan; Supporting student mental health; Shaping classroom dynamics; Social anxiety in classroom; Statements of teaching philosophy.}
        \end{itemize}
      \resumeItemListEnd
      
    \resumeSubheading
      {University of Waterloo}{Waterloo, Canada}
      {Teaching Assistant}{2020 - 2022}
      \resumeItemListStart
      \resumeItem{Linear Signals and System – BME 252 - [Spring 2022].}
      \resumeItem{Algorithms and Data Structures – MTE140 - [Winter 2022].}
      \resumeItem{Linear Signals and System – SYDE 252 - [Fall 2021].}
      \resumeItem{Linear Signals and System – BME 252 - [Spring 2021].}
      \resumeItem{Intro to Complex Systems - SYDE 532 - [Winter 2021].}
      \resumeItem{Digital Computation - SYDE 121 - [Fall 2020].}
      \resumeItem{Pattern Recognition - SYDE 675 - [Winter 2020].}
      \resumeItemListEnd

    \resumeSubheading
      {Shiraz University}{Shiraz, Iran}
      {Teaching Assistant}{2012 - 2016}
      \resumeItemListStart
        \resumeItem{Advanced Pattern Recognition [Spring 2016].}{}
        \resumeItem{Computer Vision [2014 - 2015].}{}
        \resumeItem{Statistical Pattern Recognition [Fall 2012].} {}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%--------Awards------------
\section{Awards}
\resumeSubHeadingListStart
    \resumeSubheading
    {Best Paper Award in the Hockey Analytics Conference}{Linköping, Sweden.}{Buzko K., Nazemi A., Clausi DA., Chen Y. Ice Hockey Action Recognition via Contextual Priors.}{2025} 

    \resumeSubheading
    {International Doctoral Student Award }{Waterloo, Canada}{By University of Waterloo.}{2019 - 2023} 

    \resumeSubheading
    {CVPR Challenge Finalist}
    {Virtual}
    {Tong J, Nazemi A, Shafiee M, Fieguth P. CLVision 2020 Challenge Solution.}{2020} 

    \resumeSubheading
      {Iran Police National Traffic Safety Award} {Tehran, Iran}
      {for "Iranian on road vehicles Make and Model Recognition System".}
      {2015}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
 \section{Research Experience}
   \resumeSubHeadingListStart

    \resumeSubheading
    {University of Waterloo}{Waterloo, Canada}{Research Collaboration}{2020 - present}
    \resumeItemListStart
    \resumeItem{\textbf{Stathletes Inc - [2024 - present]}}
        \begin{itemize}
        \item{Ice hockey broadcast video analysis.} 
        \end{itemize}

      \resumeItem{\textbf{Moonrise Medical Inc - [2023 - 2024]}}
    \begin{itemize}
    \item{Developing Machine Learning models on Doppler ultrasound data.} 
    \end{itemize}

      \resumeItem{\textbf{Microsoft Office Media Group - [2020 - 2024]}}
    \begin{itemize}
    \item{Machine Learning for visual relation detection.}
    \item{Semi-supervised video object segmentation.}
    \end{itemize}

    \resumeItem{\textbf{Nutrition and Dietary Research Group - [2021 - present]}}
    \begin{itemize}
    \item{A University of Waterloo multidisciplinary research project.}
    \item{AI modeling of dietary intakes in the presence of measurement error.}
    \item{AI for estimating usual intake distributions of multiple dietary components.}
    \end{itemize}
    \resumeItemListEnd

    \resumeSubheading
      {Waterloo Artificial Intelligence Institute (Waterloo.ai)}{Waterloo, Canada}
      {Research Assistance}{2019 - 2020}
      \resumeItemListStart
      \resumeItem{{Collaboration with ETRI of South Korea.}}
          {}
        \begin{itemize}
            \item{Mitigating catastrophic forgetting on CNN models.}
        \end{itemize}
      \resumeItemListEnd

     \resumeSubheading
      {INRIA STARS Team}{Sophia Antipolis, France}
      {Research Intern}{2017 – 2018}
      \resumeItemListStart
      \resumeItem{{Recognizing human actions using RGB videos.}}
          {}
      \resumeItemListEnd

     \resumeSubheading
      {IPM - Institute for Research in Fundamental Sciences}{Tehran, Iran}
      {Research Assistance}{2013 - 2014}

      \resumeSubheading
      {CVPR Lab – Shiraz University}{Shiraz, Iran}
      {Research Assistance}{2011 - 2017}
     
  \resumeSubHeadingListEnd

%-----------MENTORSHIP-----------------
 \section{Mentorship}
   \resumeSubHeadingListStart

        \resumeSubheading
      {University of Waterloo}{Waterloo, Canada}
      {Graduate Research Assistants}{2024 - present}
      \resumeItemListStart
          \resumeItem{{Co-mentoring 2 PhD and 6 master students in the sport analytics group.}}
          {}
        \begin{itemize}
            \item{Utilizing Kanban methods such as Jira for the academic project management.}
        \end{itemize}  
      \resumeItemListEnd
   
    \resumeSubheading
      {University of Waterloo}{Waterloo, Canada}
      {Graduate Research Assistants}{2023 - 2024}
      \resumeItemListStart
        \resumeItem{{Sepehr Ghavam - [Winter 2024]}}
          {}
        \begin{itemize}
            \item{Video object segmentation for long videos.}
        \end{itemize}  
      \resumeItem{{Simon Frew - [Winter 2023]}}
          {}
        \begin{itemize}
            \item{Neural networks on dietary data with measurement error.}
        \end{itemize} 
      \resumeItemListEnd

    \resumeSubheading
      {University of Waterloo}{Waterloo, Canada}
      {Undergraduate Research Assistants}{2020 - 2024}
      \resumeItemListStart
        \resumeItem{{Stephie Liu - [Spring 2025]}}
          {}
        \begin{itemize}
            \item{Rink agnostic homography estimation for Ice Hockey.}
        \end{itemize}  
        \resumeItem{{Jonathan Dumanski - [Winter 2025]}}
          {}
        \begin{itemize}
            \item{Rink agnostic homography estimation for Ice Hockey.}
        \end{itemize}  
        \resumeItem{{Soyeon Jang - [Winter 2024]}}
          {}
        \begin{itemize}
            \item{Doppler Ultrasound image classification.}
        \end{itemize}  
      \resumeItem{{Michael Frew - [Fall 2023]}}
          {}
        \begin{itemize}
            \item{Doppler Ultrasound data analysis.}
        \end{itemize}        
      \resumeItem{{Xin Xue - [Fall 2023]}}
          {}
        \begin{itemize}
            \item{Continual learning on custom diffusion model.}
        \end{itemize}      
      \resumeItem{{Zeyad Moustafa - [Spring 2023]}}
          {}
        \begin{itemize}
            \item{Designing a long video object segmentation dataset for continual learning.}
        \end{itemize}
      \resumeItem{{David Eric Austin - [Winter 2022]}}
          {}
        \begin{itemize}
            \item{Neural networks on dietary data.}
        \end{itemize}
      \resumeItem{{Anita Hu - [Spring 2020]}}
          {}
        \begin{itemize}
            \item{Continual learning for classification tasks.}
        \end{itemize}    
      \resumeItemListEnd

        \resumeSubheading
      {University of Waterloo}{Waterloo, Canada}
      {Undergraduate Capstone Project}{2025 - present}
      \resumeItemListStart
          \resumeItem{{Supervising a team of 6 undergrad students.}}
          {}
        \begin{itemize}
            \item{An LLM based coach assistant questioning and answering system via the RAG architectural approach.}
        \end{itemize}  
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%----------- Professional experiences
 \section{Professional Experience}
   \resumeSubHeadingListStart
    \resumeSubheading
    {Shiraz University | Industrial Projects}{Shiraz, Iran}{Management and Development}{2012 - 2017}
    \resumeItemListStart
      \resumeItem{\textbf{Vision-Based Vehicle Speed Estimation (Using a single camera) - [2015 - 2017]}}
    \begin{itemize}
        \item{Role: \textbf{Project manager.}}
    \item{Spearheaded a major initiative for Shiraz University in collaboration with Shiraz municipality.} 
    \item{Led the development of 10 cutting-edge hardware and software vision-based speed estimation systems.} 
    \end{itemize}

      \resumeItem{\textbf{Iranian on-road vehicles Make and Model Recognition (MMR) System - [2012 - 2014]}}
    \begin{itemize}
    \item{Role: \textbf{Main contributor}}
    \item{A Shiraz University project for vehicle MMR of 50 vehicle models.}
    \end{itemize}

    \resumeItem{\textbf{License Plate Recognition (LPR) and Optical Character Recognition (OCR) - [2012 - 2013]}}
    \begin{itemize}
    \item{Role: \textbf{Developer}}
    \item{Working on fast feature learning methods.}
    \end{itemize}
    \resumeItemListEnd
    
    \resumeSubheading
      {Fars Science and Technology Park (FSTP) }{Shiraz, Iran}
      {Co-founder}{2013 - 2015}
        \resumeItemListStart
      \resumeItem{{Pars Tadbir Intelligent Processing Co.}}
    \begin{itemize}
    \item{Virtual showroom platform powered by AI and augmented reality (AR) technology.}  
    \end{itemize}
      \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------Publications-----------------
 \section{Publications}
 \resumeItemListStart
    \item {Buzko K.,~\textbf{Nazemi A.}, Clausi DA., Chen Y. Position Paper: Ice Hockey Action Recognition via Contextual Priors. In Linköping Hockey Analytics Conference. 2025. (~\textbf{Best Paper Award})}

    \item {Iaboni E., Negulescu S., Pitassi M.,~\textbf{Nazemi A.}, Bright J., Chomko V., Clausi DA., Dickinson S., Brecht T. Position Paper: New Views of Shots-Towards Measures of Net Visibility and Reachability. In Linköping Hockey Analytics Conference. 2025.}
    
    \item {Salass L., Bright J., Fieguth P.~\textbf{Nazemi A.}, Chen Y., Zelek J., Clausi D. In Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2025.}
    
    \item {Spicker D., \textbf {Nazemi A.}, Hutchinson J., Fieguth P., Kirkpatrick S.I., Wallace M., Dodd K.W. Challenges for Predictive Modeling With Neural Network Techniques Using Error‐Prone Dietary Intake Data. Statistics in Medicine, 2025.}

    \item {\textbf {Nazemi, A.}, Sepanj, M.H., Pellegrino, N., Czarnecki, C. and Fieguth, P. Particle-Filtering-based Latent Diffusion for Inverse Problems. arXiv preprint, 2024.}
    
    \item {\textbf {Nazemi, A.}, Shafiee, M.J., Gharaee, Z. and Fieguth, P. Memory-Efficient Continual Learning Object Segmentation for Long Videos. IEEE Access. 2024}

    \item {Sepanj, M. H., \textbf {Nazemi, A.}, Preston, C., Lee, A. M. and Fieguth, P. From Single Shot to Structure: End-to-End Network-Based Deflectometry for Specular Free-Form Surface Reconstruction. Applied Sciences, 2024.}

    \item {\textbf {Nazemi, A}. Continual learning-based Video Object Segmentation.[Doctoral dissertation, University of Waterloo], UWSpace, 2023.~\href{http://hdl.handle.net/10012/19583}{\underline{http://hdl.handle.net/10012/19583}}}

    \item{\textbf {Nazemi, A.}, Moustafa, Z., Fieguth, P. Clvos23: A long video object segmentation dataset for continual learning. In Proceedings of the IEEE/CVF Conference on Computer Vision and Pattern Recognition. 2023.}

    \item{Shafiee, M. J., Jeddi, A., \textbf {Nazemi, A.}, Fieguth, P., Wong, A. "Deep Neural Network Perception Models and Robust Autonomous Driving Systems: Practical Solutions for Mitigation and Improvement." IEEE Signal Processing Magazine 38.1 (2020): 22-30.}

    \item{\textbf {Nazemi, A.}, Fieguth, P. "Identifying threatening samples for adversarial robustness," Safety and Robustness in Decision Making — NeurIPS 2019 workshop, Vancouver, 2019.}

    \item{\textbf {Nazemi, A.}, Fieguth, P. "Potential adversarial samples for white-box attacks," ML with guarantees NeurIPS 2019 workshop, Vancouver, 2019}

    \item{\textbf {Nazemi, A.}, Azimifar, Z., Shafiee, M.J., Wong, A. Real-Time Vehicle Make and Model Recognition Using Unsupervised Feature Learning. IEEE Transactions on Intelligent Transportation Systems. 2019.}

    \item{\textbf {Nazemi, A.}, Kamyab, S., Azimifar, Z., Fieguth, P. Human Perception-based Image Enhancement Using a Deep Generative Model. Journal of Computational Vision and Imaging Systems. 2018 Dec 24;4(1):3-.}

    \item{\textbf {Nazemi, A.}, Azimifar, Z. "Locality hash-table constrain linear coding for fast image classification." Computer Society of Iran Computer Conference (CSICC), 2015, Iran (In Persian).}

    \item{\textbf {Nazemi} et. al. "The Impact of Microsoft Kinect on Business Model Innovation." 18th Annual Asian Science Park Association (ASPA) international conference, 2014, Shiraz-Iran.}

    \item{\textbf {Nazemi, A.}, Azimifar, Z. "Assessment of Photo Aesthetics via Sparse Coding." International Conference of Cognitive Science (ICCS), 2013 5th 7-9 May 2013, Tehran – Iran.} 

    \item{\textbf {Nazemi, A.}, Shafiee, M.J., and Azimifar, Z. "On road vehicle make and model recognition via sparse feature coding." Machine Vision and Image Processing (MVIP), 2013 8th Iranian Conference on. IEEE, 2013.} 
      \resumeItemListEnd

%-----------References-----------------
 \section{References}
\begin{itemize}
    \item {References available upon request.}
\end{itemize}

%-------------------------------------------
\end{document} 